---
title: "Sliding windows"
opengraph:
  image: 
    src: "figures_articles/automatic_tabs.png"
  twitter:
    creator: "@rafa_zamr"
    card: summary_large_image
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sliding windows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

ðŸŒ Functions related to the calculation of distance between geographic points and data partitioning in sliding windows.

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```


# Libraries ðŸ“š

```{r }
 library(modeltime)
 library(rsample)
 library(parsnip)
 library(recipes)
 library(workflows)
 library(dplyr)
 library(tidyr)
 library(sknifedatar)
```

## Function sliding_window ðŸ”

This feature allows you to apply a monthly moving sliding window transformation on a data set. The number of folds and the types of variables to be calculated are defined. For a detailed explanation and use case of this function with R code, see [Crime occurrence prediction / sliding_window](https://rafael-zambrano-blog-ds.netlify.app/posts/2020-12-22-prediccin-de-delitos-en-caba/#aplicaci%C3%B3n-de-ventanas-deslizantes).

```{r}
pliegues = 1:13
names(pliegues) = pliegues

variables = c("delitos", "temperatura", "mm_agua", "lluvia", "viento")
names(variables) = variables

data_longer_crime %>% head()
```

```{r}

sliding_window(data = data_longer_crime %>% dplyr::select(-c(long,lat)),
               inicio = 13,
               pliegues = pliegues,
               variables = variables)
```


To consult projects where this functions was used, visit:

* [Crime occurrence prediction](https://rafael-zambrano-blog-ds.netlify.app/posts/2020-12-22-prediccin-de-delitos-en-caba/)


